Issues with Dynamical Measurements Across the Disk

### 2019-02-17 paper/ms.tex
Minor fix to thick-disk label

\begin{figure*}
\plotone{fig/schmactions_one_orbit.pdf}
\caption{The artificial phase-dependence in the observed actions induced by an
error in the Galactocentric coordinate system. We consider here the thick disk
orbit, which has actions of $(J_r, L_z, J_z) = (37.9, -1520, 7.0)\,\actunit$
and $z_{\text{max}}=850\,\pc$ (see Table~\ref{tab:orbits}). We integrate the
orbit according to the procedure laid out in Section~\ref{ssec:action_comp}.
Then, we subtract $100\,\pc$ from the $z$ value ({\em upper panels}) or the
$x$ value ({\em lower panels}) of each position in the orbit, corresponding to
an erroneous observer assuming a midplane ({\em upper}) or solar radius ({\em
lower}) that is off by $100\,\pc$. We then allow our (immortal) observer to
observe the orbit over $1\,\Gyr$ and perform the same orbit integration
procedure at each timestep, and report the values of the actions. The
computation of $L_z$ is pristine to errors in $z$, with only numerical
artifacts remaining. Only small errors are induced in $J_r$, with the middle
$90\%$ of values over the $\Gyr$ being within $\sim8\%$ of the true $J_r$. As
expected, large errors are induced in $J_z$ with a $100\,\pc$ offset in $z$,
with the middle $90\%$ of values being within $\sim43\%$ of the true $J_z$. The $x$
offset induces uncertainties in $J_r$ and $L_z$ of $\sim21\%$ and $\sim3\%$,
respectively. A $\sim3\%$ error in $J_z$ is also induced.}
\label{fig:one_orbit_wrong_ref}
\end{figure*}

>>>>

\begin{figure*}
\plotone{fig/schmactions_one_orbit.pdf}
\caption{The artificial phase-dependence in the observed actions induced by an
error in the Galactocentric coordinate system. We consider here the thick-disk
orbit, which has actions of $(J_r, L_z, J_z) = (37.9, -1520, 7.0)\,\actunit$
and $z_{\text{max}}=850\,\pc$ (see Table~\ref{tab:orbits}). We integrate the
orbit according to the procedure laid out in Section~\ref{ssec:action_comp}.
Then, we subtract $100\,\pc$ from the $z$ value ({\em upper panels}) or the
$x$ value ({\em lower panels}) of each position in the orbit, corresponding to
an erroneous observer assuming a midplane ({\em upper}) or solar radius ({\em
lower}) that is off by $100\,\pc$. We then allow our (immortal) observer to
observe the orbit over $1\,\Gyr$ and perform the same orbit integration
procedure at each timestep, and report the values of the actions. The
computation of $L_z$ is pristine to errors in $z$, with only numerical
artifacts remaining. Only small errors are induced in $J_r$, with the middle
$90\%$ of values over the $\Gyr$ being within $\sim8\%$ of the true $J_r$. As
expected, large errors are induced in $J_z$ with a $100\,\pc$ offset in $z$,
with the middle $90\%$ of values being within $\sim43\%$ of the true $J_z$. The $x$
offset induces uncertainties in $J_r$ and $L_z$ of $\sim21\%$ and $\sim3\%$,
respectively. A $\sim3\%$ error in $J_z$ is also induced.}
\label{fig:one_orbit_wrong_ref}
\end{figure*}
